### 2022-03-24 draft.tex
Deploying to gh-pages from @ emuise/ms-assessingRepresentation@fcb3e3ba0845866a4bd4386cdbd7ae8b609d7e01 🚀

The province of British Columbia, Canada, covers 94.4 million ha, of
which approximately 64\% is forested (BC Ministry of Forests 2003), and
encapsulates a wide variety of biomes and ecosystems. This diversity of
ecosystems is in part due to the large area as well as variations in
topography and climate. The existing Biogeoclimatic Ecosystem
Classification (BEC) system disaggregates BC ecosystems into zones
(Pojar et al. 1987). The broadest classification delineates 16 zones,
which are further broken down into subzones, variants, and phases based
on microclimate, precipitation, and topography (Pojar et al. 1987,
Meidinger and Pojar 1991). As a result, BEC zones vary widely in size
(ranging from 0.25 million ha to 17.5 million ha), and in number of
subzones (from 1 to 43; see (\textbf{tab:bec-table?})).

@@

Zone

Elevation Covariance

Canopy Cover (\%)

Canopy Height (m)

PA

UA

\% Difference

PA

UA

\% Difference

PA

UA

\% Difference

BAFA

0.39

0.39

0.01\%

46.94\%

48.47\%

3.17\%

14.03

13.11

-7\%

BG

0.38

0.38

-1.41\%

61.8\%

58.71\%

-5.26\%

23.00

21.58

-6.59\%

BWBS

0.37

0.38

2.62\%

67.18\%

64.72\%

-3.8\%

15.83

15.69

-0.9\%

CDF

0.31

0.33

6.35\%

89.38\%

83.69\%

-6.79\%

27.35

26.58

-2.89\%

CMA

0.38

0.39

1.63\%

62.65\%

64.01\%

2.13\%

19.91

20.01

0.48\%

CWH

0.34

0.33

-3.83\%

83.94\%

85.26\%

1.55\%

21.58

22.34

3.4\%

ESSF

0.37

0.37

0.34\%

61.7\%

64.97\%

5.04\%

18.90

18.91

0.07\%

ICH

0.36

0.36

-1.75\%

81.24\%

83.52\%

2.73\%

22.39

22.18

-0.98\%

IDF

0.36

0.36

-0.3\%

67.42\%

67.9\%

0.71\%

21.98

22.49

2.29\%

IMA

0.38

0.36

-3.72\%

68.17\%

62.07\%

-9.83\%

22.53

21.06

-6.98\%

MH

0.36

0.36

0.25\%

76.87\%

77.85\%

1.26\%

19.42

18.31

-6.07\%

MS

0.35

0.35

0.31\%

57.99\%

60.41\%

4.01\%

20.64

20.86

1.04\%

PP

0.36

0.37

0.25\%

57.92\%

48.93\%

-18.36\%

19.88

18.03

-10.24\%

SBPS

0.36

0.35

-1.97\%

32.98\%

34.63\%

4.76\%

18.00

18.70

3.75\%

SBS

0.37

0.37

-0.4\%

62.24\%

67.25\%

7.45\%

18.51

18.67

0.82\%

SWB

0.39

0.39

-1.22\%

56.67\%

57.71\%

1.8\%

13.78

13.67

-0.83\%

: Mean values of forest structural attributes in protected areas (PA),
unprotected areas (UA), as well as the percent difference between the
means. Zones with more than a 5\% difference are bolded.
\{\#tbl:vector-table\}

>>>>

The province of British Columbia, Canada, covers 94.4 million ha, of
which approximately 64\% is forested (BC Ministry of Forests 2003), and
encapsulates a wide variety of biomes and ecosystems. This diversity of
ecosystems is in part due to the large area as well as variations in
topography and climate. The existing Biogeoclimatic Ecosystem
Classification (BEC) system disaggregates BC ecosystems into zones
(Pojar et al. 1987). The broadest classification delineates 16 zones,
which are further broken down into subzones, variants, and phases based
on microclimate, precipitation, and topography (Pojar et al. 1987,
Meidinger and Pojar 1991). As a result, BEC zones vary widely in size
(ranging from 0.25 million ha to 17.5 million ha), and in number of
subzones (from 1 to 43; see tbl.~\ref{tbl:bec-table}).

@@

\hypertarget{tbl:vector-table}{}
\begin{longtable}[]{@{}cccccccccc@{}}
\caption{\label{tbl:vector-table}Mean values of forest structural
attributes in protected areas (PA), unprotected areas (UA), as well as
the percent difference between the means. Zones with more than a 5\%
difference are bolded.}\tabularnewline
\toprule
\begin{minipage}[b]{0.04\columnwidth}\centering
Zone\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\centering
Elevation Covariance\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\centering
Elevation Covariance\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\centering
Elevation Covariance\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\centering
Canopy Cover (\%)\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\centering
Canopy Cover (\%)\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\centering
Canopy Cover (\%)\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\centering
Canopy Height (m)\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\centering
Canopy Height (m)\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\centering
Canopy Height (m)\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.04\columnwidth}\centering
Zone\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\centering
Elevation Covariance\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\centering
Elevation Covariance\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\centering
Elevation Covariance\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\centering
Canopy Cover (\%)\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\centering
Canopy Cover (\%)\strut
\end{minipage} & \begin{minipage}[b]{0.07\columnwidth}\centering
Canopy Cover (\%)\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\centering
Canopy Height (m)\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\centering
Canopy Height (m)\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\centering
Canopy Height (m)\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.04\columnwidth}\centering
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
PA\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
UA\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\% Difference\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
PA\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
UA\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
\% Difference\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
PA\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
UA\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
\% Difference\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\centering
BAFA\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.39\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.39\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.01\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
46.94\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
48.47\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
3.17\%\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
** 14.03 **\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
** 13.11 **\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
** -7\% **\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\centering
BG\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.38\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.38\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
-1.41\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
** 61.8\% **\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
** 58.71\% **\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
** -5.26\% **\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
** 23.00 **\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
** 21.58 **\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
** -6.59\% **\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\centering
BWBS\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.37\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.38\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
2.62\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
67.18\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
64.72\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
-3.8\%\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
15.83\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
15.69\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
-0.9\%\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\centering
CDF\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
** 0.31 **\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
** 0.33 **\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
** 6.35\% **\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
** 89.38\% **\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
** 83.69\% **\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
** -6.79\% **\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
27.35\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
26.58\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
-2.89\%\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\centering
CMA\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.38\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.39\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
1.63\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
62.65\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
64.01\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
2.13\%\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
19.91\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
20.01\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.48\%\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\centering
CWH\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.34\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.33\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
-3.83\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
83.94\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
85.26\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
1.55\%\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
21.58\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
22.34\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
3.4\%\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\centering
ESSF\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.37\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.37\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.34\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
** 61.7\% **\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
** 64.97\% **\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
** 5.04\% **\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
18.90\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
18.91\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.07\%\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\centering
ICH\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.36\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.36\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
-1.75\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
81.24\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
83.52\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
2.73\%\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
22.39\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
22.18\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
-0.98\%\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\centering
IDF\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.36\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.36\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
-0.3\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
67.42\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
67.9\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
0.71\%\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
21.98\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
22.49\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
2.29\%\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\centering
IMA\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.38\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.36\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
-3.72\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
** 68.17\% **\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
** 62.07\% **\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
** -9.83\% **\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
** 22.53 **\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
** 21.06 **\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
** -6.98\% **\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\centering
MH\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.36\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.36\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.25\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
76.87\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
77.85\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
1.26\%\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
** 19.42 **\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
** 18.31 **\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
** -6.07\% **\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\centering
MS\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.35\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.35\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.31\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
57.99\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
60.41\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
4.01\%\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
20.64\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
20.86\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
1.04\%\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\centering
PP\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.36\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.37\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.25\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
** 57.92\% **\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
** 48.93\% **\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
** -18.36\% **\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
** 19.88 **\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
** 18.03 **\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
** -10.24\% **\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\centering
SBPS\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.36\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.35\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
-1.97\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
32.98\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
34.63\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
4.76\%\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
18.00\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
18.70\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
3.75\%\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\centering
SBS\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.37\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.37\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
-0.4\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
** 62.24\% **\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
** 67.25\% **\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
** 7.45\% **\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
18.51\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
18.67\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.82\%\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.04\columnwidth}\centering
SWB\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.39\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
0.39\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
-1.22\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
56.67\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
57.71\%\strut
\end{minipage} & \begin{minipage}[t]{0.07\columnwidth}\centering
1.8\%\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
13.78\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
13.67\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\centering
-0.83\%\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}
